---
title: "Models"
author: "Ronit Dash"
format: html
execute:
  echo: false
---

```{r}
#| label: model
#| cache: true
poll_data <- tibble(biden = c(rep(1, 655),                        rep(0, 904)))

fit_bern <- brm(formula = biden ~ 1, data = poll_data, family = bernoulli(), refresh = 0, 
silent = 2, seed = 9)

```

```{r}
#| label: setup
#| message: FALSE
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: plot
ndata <- tibble(.rows = 1)
fit_bern |> add_epred_draws(newdata = ndata) |> select(.epred) |> 
ggplot(aes(x = .epred)) + geom_density(aes(y = after_stat(count / sum(count)))) + 
scale_x_continuous(labels = scales::percent_format()) + labs(title = expression(paste("Posterior Probability Distribution of ", rho)),
         subtitle = "Distribution is centered at 42%",
         x = expression(paste("Proportion, ", rho, ", of Biden Voters")),
         y = "Probability") + 
scale_y_continuous(labels = scales::percent_format())
```

Using data from a March 2024 poll from YouGov consisting of 1559 US Citizens, we seek to determine the proportion of voters that will pick Joe Biden as their candidate in the 2024 election. One problem with this approach is that Biden's approval ratings may change too much over time. In the poll, Biden has support less than 50%. According to how Biden's approval ratings change, the percentage distribution of his votes were 42%, with a 95% confidence interval being between 22 and 42%.

$$ biden_i =  \mu + \epsilon_i $$
```{r}
slice_sample(poll_data, n = 10)
```

```{r}
tbl_regression(fit_bern, intercept = TRUE)
```


